Mire microclimate: groundwater buffers temperature in waterlogged versus dry soils

### 2020-10-12 doc/manuscript.Rmd
minor address change
zenodo doi

---
title: "Mire microclimate: groundwater buffers temperature in waterlogged versus dry soils"
subtitle: "Short title: Testing the thermal buffer of mire groundwater"
output: github_document
bibliography: refs.bib
biblio-style: international-journal-of-climatology.csl
link-citations: yes
always_allow_html: true
---

@@

Eduardo Fernández-Pascual^1^ ^+^, Eva Correia-Álvarez^2^

^1^ Universidad de Oviedo, ^2^ Independent researcher

@@

# Keywords

bog, CHELSA, climatic model, datalogger, fen, peatland, soil temperature, wetland

@@

The original data, as well as the R code for the analysis and creation of the manuscript, can be accessed at the GitHub repository https://github.com/efernandezpascual/mires. Upon publication, a version of record of the repository will be deposited in Zenodo.

>>>>

---
title: "Mire microclimate: groundwater buffers temperature in waterlogged versus dry soils"
output: github_document
bibliography: refs.bib
biblio-style: international-journal-of-climatology.csl
link-citations: yes
always_allow_html: true
---

@@

Eduardo Fernández-Pascual^1^ ^+^, Eva Correia-Álvarez^1^

^1^ Universidad de Oviedo

@@

**Keywords:** bog, CHELSA, climatic model, datalogger, fen, peatland, soil temperature, wetland

@@

The original data, as well as the R code for the analysis and creation of the manuscript, can be accessed at the GitHub repository https://github.com/efernandezpascual/mires. A version of record of the repository can be found at https://doi.org/10.5281/zenodo.4081418.
